Tensor anisotropy as a tracer of cosmic voids

### 2015-06-11 RefereeResponse.md

    Response: 
    - We have added a clearer explanation of the ridge removing procedure (3rd paragraph of subsec. 3.3).

4. **In Fig. 6, I only see a clear ridge in FA at r~r_eff in a few cases. the sentence in Sect. 5.5 "The 
    difference between the radius where the density ridge is reached ([r/]reff = 3) and the radius of the 
    FA ridge ([r/]reff = 1 ) ..." implies that I should see a ridge in FA at r~r_eff. Is this because the 
    ridge is actually a 2D surface that is spherically averaged? It would be helpful to point this (or any 
    other reasons) out. Also, the statement "This makes the FA ridge a reasonable boundary for voids compared 
    to the traditional definition that puts the boundary at the density ridge" implies (perhaps 
    unintentionally) that the FA ridge is a superior marker of the edge of a void than a density ridge. It is 
    a physically different sort of ridge, and I agree that it is reasonable, but I do not see why it should 
    be superior.**

5. **I am not convinced that the "tiny white bubbles located inside
sheets" are embedded in overdense regions.  Based just on Fig. 1, they
could be physical, but small, voids. We also no nothing of their
extent  perpendicular to the plane of Fig. 1; we could just be looking
of corners of much larger objects.**

    Response:
    - In the right panels of Fig. 1, the color of each void refers now
    the effective radius. The size could be inferred from the
    figure. We have checked by visual inspection some cases and small
    voids are indeed located inside sheets and filaments. This was
    already found and explained in Hoffman et al. 2012.

### 2015-06-11 cosmic_voids.tex
solved issue #14

The difference between the radius where the density ridge is reached 
($r/\reff =3$) and the radius of the FA  ridge ($r/\reff =1$ )
justifies in a more quantiative way the qualitative argument
we present in sub-section \ref{subsec:watershed} to define void boundaries in
our method.  
Namely that as we increase the void boundary, we reach
first middle density walls, before reaching high density structures
associated with high anisotropy. 
This makes the FA ridge a reasonable
boundary for voids compared to the traditional definition that puts
the boundary at the density ridge.

>>>>

The difference between the radius where the density ridge is reached 
($r/\reff =3$) and the radius of the FA maxima ($r/\reff =1$, most
manifest in the T-Web voids) justifies in a more quantiative way the
qualitative argument we present in sub-section \ref{subsec:watershed}
to define void boundaries in our method.  
Namely that as we increase the void boundary moving away from the
center, we reach first middle density walls, before reaching high
density structures associated with high anisotropy.  
This implies that voids defined with the FA never present positive
overdensities, making the FA maximum a reasonable boundary for voids
compared to the traditional definition that puts the boundary at the
densityridge.
